---
title: "Hello R"
author: "Nyah Rey"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 6
    fig_height: 6
    highlight: pygments
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

### Exercise 1

There are 142 row and 24 variables included. The variables included are x/y values for away, bullseye, circle, dino, dots, h lines, high lines, slant down/up, star, v lines, w lines and x/y shape. 

### Exercise 2

First plot the data in the dino dataset:

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) + geom_point()
```

Calculate the correlation between `x` and `y` in the dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First plot the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) + geom_point()

```

Calculate the correlation between `x` and `y` in the dataset:

```{r cor-star}

star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

First plot the data in the circle dataset:


```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) + geom_point()

```

Calculate the correlation between `x` and `y` in the dataset:

```{r}
circle_data %>%
  summarize(r = cor(x, y))

```

### Exercise 5
Plot all datasets and calcuate their summer correlation coefficients. 

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")

datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
## `summarise()` ungrouping output (override with `.groups` argument)
## # A tibble: 13 x 2
## dataset r
##
## 1 away -0.0641
## 2 bullseye -0.0686
## 3 circle -0.0683
## 4 dino -0.0645
## 5 dots -0.0603
## 6 h_lines -0.0617
## 7 high_lines -0.0685
## 8 slant_down -0.0690
## 9 slant_up -0.0686
## 10 star -0.0630
## 11 v_lines -0.0694
## 12 wide_lines -0.0666
## 13 x_shape -0.0656

```